Scale Space Edge Detection

### 2018-03-10 paper.tex
updated equation format
Add results section

\section{Defining an Edge in Scale Space}
A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as \cite{Lindeberg1998}
\begin{equation}
  \begin{pmatrix}
    \cos{\alpha} \\
    \sin{\alpha}
  \end{pmatrix}
  = \frac{1}{\sqrt{L_x^2+L_y^2}}
  \begin{pmatrix}
    L_x \\
    L_y
  \end{pmatrix}
  \Bigg|_{(x_0,y_0)}
\end{equation}
With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
\begin{align}
  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
\end{align}
So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. The results for $L_v$ can be found on page \pageref{t_v}. So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}
The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}
The results for $L_{vv}$ can be found on page \pageref{t_vv}.
The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
\begin{equation} \label{eq:c2}
  \begin{aligned}
    \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
    \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
  \end{aligned}
\end{equation}
Then equation \ref{eq:c1} in conjunction with \ref{eq:c2} form the neccessary constraints for us to define an edge in the scale space.
Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.

@@

>>>>

\section{Defining an Edge in Scale Space}
A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as \cite{Lindeberg1998}
\begin{equation}
  \begin{pmatrix}
    \cos{\alpha} \\
    \sin{\alpha}
  \end{pmatrix}
  = \frac{1}{\sqrt{L_x^2+L_y^2}}
  \begin{pmatrix}
    L_x \\
    L_y
  \end{pmatrix}
  \Bigg|_{(x_0,y_0)}
\end{equation}
With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
\begin{align}
  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
\end{align}
So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. The results for $L_v$ can be found on page \pageref{t_v}. So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}
The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}
The results for $L_{vv}$ can be found on page \pageref{t_vv}.
The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
\begin{equation} \label{eq:c2}
  \begin{aligned}
    \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
    \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
  \end{aligned}
\end{equation}
Then (Eq. \ref{eq:c1}) in conjunction with (Eq. \ref{eq:c2}) form the necessary constraints for us to define an edge in the scale space.
Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.

@@

\section{Results}
\subsection{Diffuse and sharp edges in the same photo}
To demonstrate the results of our program, we will use the following test image.
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_orig.jpg}
  \caption{Block test image}
  \label{block_orig}
\end{figure}

Here is the result of thresholding the gradient as calculated by the Sobel operator for this image:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/sobel_block.jpg}
  \caption{The edges of the block image according to the Sobel gradient}
  \label{block_sobel}
\end{figure}

In contrast, our edge detection algorithm produces the following result:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_final.png}
  \caption{The final output of our program on the block image}
  \label{block_final}
\end{figure}
The edge of the shadow is clearly present in the image, a clear improvement over the Sobel gradient of the image.
Unfortunately, the edge of the shadow is not a continuous path.
This is due to spurious fragmentation of the edge in our marching cubes algorithm due to our inability to resolve ambiguous situations.
We can see this by displaying the full set of edges:
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.3]{Images/block/block_all_edges.png}
  \caption{All edges of the block image as detected by our program}
  \label{block_final}
\end{figure}
In this image, we see that the full edge of the shadow is captured, although there are also many spurious images formed by structures in the background that we do not want to detect.

\subsection{Other results}
Subjectively, our results seem quite reasonable for the given inputs.
Further improvement can be made to fix spurious edge segmentation in the future.
\begin{table}[H]
  \caption{Results of running our program on other images}
  \label{t_vvv}
  \centering
  \tabulinesep=0.3em
  \begin{tabu}to \textwidth{X[c,m]X[c,m]}
    \toprule
    Original & Result\\
    \midrule
    \includegraphics[height=18em]{{{Images/lena/lena_orig}}} & \includegraphics[height=18em]{{{Images/lena/lena_final}}} \\
    \includegraphics[height=18em]{{{Images/mandrill/mandrill_orig}}} & \includegraphics[height=18em]{{{Images/mandrill/mandrill_final}}} \\
    \includegraphics[height=18em]{{{Images/peppers/peppers_orig}}} & \includegraphics[height=18em]{{{Images/peppers/peppers_final}}} \\
    \bottomrule
  \end{tabu}
\end{table}
